---
title: Bar Plots
author: Brandon McKenna
date: '2017-12-04'
slug: bar-plots
categories: []
tags: []
---

Last, but not least - I'm going to cover how to create bar plots utilizing datasets within Rstudio.

First, we needed to install and load the following packages.

```{r}
library(Lahman)
library(sqldf)
library(ggplot2)
```
I'm going to use team homerun totals for all the MLB teams in 1980 to create bar plot.

```{r}
query<-"SELECT name,HR FROM Teams WHERE yearID=1980 ORDER BY HR "
result<-sqldf(query)
result$name<-factor(result$name,levels=result$name)

```

Notice something different? The last line is used for saving the results as a factor. Thus, the system knows that the order of the results should not be in alphabetical order. 
The last line is saving the information as a factor, and letting the system know that the order the results appear in the order we specified, not default alphabetical.

Once we have our data, it's time to create a bar plot. Like histograms, scatterplots and time series - ggplot2 coding is a necessity. 

```{r}
ggplot()+
  geom_bar(data=result,aes(x=name,y=HR),stat='identity')+
  coord_flip()+
  ggtitle("1980 Team Homerun Totals")+
  xlab("Team Name")+
  ylab("Homeruns")

```

There you go, a bar plot! Coding can be much easier than expected. I hope these previous lessons helped. Thanks for tuning in. 