---
title: Scatter Plots
author: Brandon McKenna
date: '2017-12-04'
slug: scatter-plots
categories: []
tags: []
---

Using Lahman and sqldf, we are going to make a scatter plot with homerun and strikeout data. 
First, install the Lahman, sqldf, and ggplot2 package!

```{r}
library(Lahman)
library(sqldf)
library(ggplot2)
```

Next, identify we have to identify our search criteria. In this instance, career homeruns and strikeouts from players who had more than 400 homeruns.

```{r}
query<-"SELECT playerID,sum(HR),sum(SO)
FROM Batting 
GROUP BY playerID
HAVING sum(HR)>400"
sqldf(query)
```
Saving for future use is helpful!

```{r}
query<-"SELECT playerID,sum(HR) AS CareerHR,sum(SO) AS CareerSO
FROM Batting
GROUP BY playerID
HAVING sum(HR)>400"
result<-sqldf(query)
```
To create a graph, we will use the ggplot coding. Homeruns will run along the y axis and strikeouts will run along the x axis. 

```{r}
ggplot()+
geom_point(data=result,aes(x=CareerSO,y=CareerHR),size=3)+
ggtitle("Career Strikeouts and Homeruns - The Best")+
xlab("Career Strikeouts")+
ylab("Career Homeruns")

```

Congratulations! You've just created a scatter plot using Rstudio. The graphing possibilities are endless if you correctly use the databases. 
